### 2021-06-10 paper/appendix_data.tex
Update a few paragraphs.

\section{Data and Parameters}
\label{sec:calibration_and_estimation}

@@

\subsection{Assortative Matching}

As mentioned in section \ref{sec:matching}, the probability that two individuals are
matched can depend on background characteristics. In particular, we allow this
probability to depend on age and county of residence. While we do not have good data on
geographical assortativity and just roughly calibrate it such that 80\% of contacts are
within the same county, we can calibrate the assortative mixing by age from the same
data we use to calibrate the number of contacts.

@@

In addition, there are some surveys that allow us to trace the expansion of employers
who offer tests to their employees. Mid march, 20\% of employers offered tests to their
employees \citep{DIHK2021}. In the second half of March, 23\% of employees reported
being offered weekly rapid tests by their employer \citep{Ahlers2021}. This share
increased to 60\% until the first days of April \cite{ZDF2021}. Until mid April 70\% of
workers were expected to receive a weekly test offer \citep{AerzteZeitung2021}. However,
according to surveys conducted in mid April \citep{Betsch2021}, less than two thirds of
individuals with work contacts receive a test offer. Starting on April 19th employers
were required by law to provide two weekly tests to their employees
\citep{Bundesanzeiger2021}. We assume that compliance is incomplete and only 80\% of
employers actually offer tests.

>>>>

\section{Data and Parameters}
\label{sec:data_and_parameters}

@@

\subsection{Contacts by age}
\label{subsec:contacts_by_age}

As mentioned in section \ref{sec:matching}, the probability that two individuals are
matched can depend on background characteristics. In particular, we allow this
probability to depend on age and county of residence. While we do not have good data on
geographical assortativity and just roughly calibrate it such that 80\% of contacts are
within the same county, we can calibrate the assortative mixing by age from the same
data we use to calibrate the number of contacts.\comment[id=HM]{Redo
\ref{fig:assortativity_other} /\ref{fig:assortativity_work} with total number of
contacts or better add a similar figure showing total number of contacts by age in all
networks}

@@

In addition, there are some surveys that allow us to trace the expansion of employers
who offer tests to their employees. Mid march, 20\% of employers offered tests to their
employees \citep{DIHK2021}. In the second half of March, 23\% of employees reported
being offered weekly rapid tests by their employer \citep{Ahlers2021}. This share
increased to 60\% until the first days of April \cite{ZDF2021}. Until mid April 70\% of
workers were expected to receive a weekly test offer \citep{AerzteZeitung2021}. However,
according to surveys conducted in mid April \citep{Betsch2021}, less than two thirds of
individuals with work contacts receive a test offer. Starting on April 19th employers
were required by law to provide two weekly tests to their employees
\citep{Bundesanzeiger2021}. We assume that compliance is incomplete and only 80\% of
employers actually offer tests.\comment[id=HM]{Can we use the IZA/BMAS survey? Not sur
about citing evening news in scientific papers.}
